DSCI 445 - Utilizing Machine Learning for Algae Predictions

### 2020-12-10 slides.Rmd
Update slides.Rmd

---
title: "DSCI 445 - Utilizing Machine Learning for Algae Predictions"
author: "Dawson Eliasen, Boston Lee, Miles Austin"
date: "12/7/2020"
output:
  beamer_presentation: default
---

@@

## Monthly

@@

## Yearly

@@

We can see that over time, during the summer, that Horsetooth is actually
becoming more blue. This isn't the case for all reservoirs, as some are
actually becoming more green. The greener they are, the more suspected algae is
in the water.

@@

$$L(y_i, F(x_i)) = (y_i = F(x_i))^2$$

>>>>

---
title: "DSCI 445 - Utilizing Machine Learning for Algae Predictions"
author: "Dawson Eliasen, Boston Lee, Miles Austin"
date: "12/11/2020"
output:
  beamer_presentation: default
---

@@

## Where did the data come from?

We are utilizing satellite data that was gathered from GEE & all in situ public
water quality data for Colorado.
  - The satellite images are collected every 14 days.
  - In situ data is collected randomly.

## A look at the monthly data

@@

## A look at the yearly data

@@

@@

$$L(y_i, F(x_i)) = (y_i - F(x_i))^2$$
